---
title       : Survey Results
subtitle    : Frquencies and Sentiment
author      : Michael Ebner
job         : Data Analyst
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## About this version of the dashboard


* This dashboards presents the results of a online survye conducted by an US-american fashion online store.
* The survey is conducted continously and new data will be added over time.
* This version of the dashboard is specially build for the peer-graded Coursera assignment and does not allow users to upload new data. The final version of the dashboard, however, will allow users to upload new data sets.
* The data has been anynomized in order to protect the client and the customers.

---

## How to use this dashboard

* Users may select 2 different views on the data: 'Frequencies' and 'Sentiment'
* The 'Frequencies' answers the question how often have certain topics been mentioned.
* The 'Sentiment' gives you an idea of the sentiment per topic or overall. The higher the sentiment score the better the sentiment.
* Simply switch between the views using the tabs on top.
* Within the views you may pick the topic of choice and split it into customer types and/or add a time dimension (month) by using the drop down menues

---

## Example of a frequency plot

```{r, message=F, warning=F, echo=F, fig.width=14, fig.height=8}
library(ggplot2)

wd <- getwd()

freq_m_c <- read.csv(paste0(wd,"/freq_m_c.csv"))


c25 <- c("dodgerblue2","#E31A1C", # red
         "green4",
         "#6A3D9A", # purple
         "#FF7F00", # orange
         "black","gold1",
         "skyblue2","#FB9A99", # lt pink
         "palegreen2",
         "#CAB2D6", # lt purple
         "#FDBF6F", # lt orange
         "gray70", "khaki2",
         "maroon","orchid1","deeppink1","blue1","steelblue4",
         "darkturquoise","green1","yellow4","yellow3",
         "darkorange4","brown")

ggplot(freq_m_c, aes(x = month, y = prop,group = topic, color = topic)) + 
         geom_line()+
         geom_point() +
         scale_y_continuous(breaks = seq(0,100, by=10), limits = c(-0,100))+
         facet_grid(customer_type~.,scales = "free")+
         scale_color_manual(values=c25)+
         labs(title = 'Proportino of Mentions by Topic',
              y = '% mentions',
              x = ' ')+
         theme_classic(base_size = 15)

```

---

## Example of a sentiment plot

```{r, message=F, warning=F, echo=F, fig.width=14, fig.height=8}
library(ggplot2)

wd <- getwd()

final <- read.csv(paste0(wd,"/final.csv"))

c25 <- c("dodgerblue2","#E31A1C", # red
         "green4",
         "#6A3D9A", # purple
         "#FF7F00", # orange
         "black","gold1",
         "skyblue2","#FB9A99", # lt pink
         "palegreen2",
         "#CAB2D6", # lt purple
         "#FDBF6F", # lt orange
         "gray70", "khaki2",
         "maroon","orchid1","deeppink1","blue1","steelblue4",
         "darkturquoise","green1","yellow4","yellow3",
         "darkorange4","brown")

       ylim <- boxplot.stats(final$ave_sentiment)$stats[c(1,5)]
       ggplot(final, aes(x=month,y=ave_sentiment,color=topic)) +
         geom_jitter(position=position_jitter(width=.1, height=0),size = .1, color = "grey")+
         geom_boxplot(alpha = .01)+
         #facet_grid(customer_type~.,scales = "free")+
         scale_y_continuous(breaks = seq(-2,2, by=.25), limits = ylim)+
         scale_color_manual(values=c25)+
         labs(title = paste0('sentiment on '),
              y = 'sentiment score',
              x = ' ',
              caption = 'outliers removed')+
         theme_classic(base_size = 15)

```